---
title: 'COVID-19 Projections for Colorado'
author: ""
date: "March 21, 2020"
output:
  html_document: default
  fig_caption: yes
  number_sections: yes
  word_document: default
  pdf_document: default
---

Comparison of R0 and intervention effectiveness (decrease in social distancing) for current interventions assumed to cause 25% reduction in social distance and 38% reduction in social distance. First case was assumed to be 1/21/2020. The separate plots within each scenario are days since first case and indicate when a change in interventions will take place (62, 67, or 72 days after the first case).

```{r, echo = F, message = F, warning = F}
op <- par()
options(width=80)
#emptyenv()
rm(list=ls())

library(knitr)
setwd('/Users/katiecolborn/OneDrive - The University of Colorado Denver/COVID19/Code')

dat <- read.csv('./allscenarios3.csv')

dat$date <- as.Date(dat$time, format="%m/%d/%Y", origin="01/21/2020")

```

#### R0 2.5 and current interventions are 25% effective

```{r, echo = F, message = F, warning = F}
dat2 <- subset(dat, R0==2.5 & phaseI==0.25)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat2) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 2.5)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat2) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 2.5)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat2) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 2.5)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())


```


#### R0 2.5 and current interventions are 38% effective

```{r, echo = F, message = F, warning = F}
dat3 <- subset(dat, R0==2.5 & phaseI==0.38)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat3) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 2.5)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat3) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 2.5)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat3) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 2.5)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### R0 3.0 and current interventions are 25% effective

```{r, echo = F, message = F, warning = F}
dat4 <- subset(dat, R0==3 & phaseI==0.25)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat4) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 3)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat4) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 3)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat4) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 3)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### R0 3.0 and current interventions are 38% effective

```{r, echo = F, message = F, warning = F}
dat5 <- subset(dat, R0==3 & phaseI==0.38)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat5) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 3)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat5) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 3)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat5) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 3)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```


#### R0 4.0 and current interventions are 25% effective

```{r, echo = F, message = F, warning = F}
dat6 <- subset(dat, R0==4 & phaseI==0.25)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat6) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 4)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat6) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 4)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat6) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 4)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### R0 4.0 and current interventions are 38% effective

```{r, echo = F, message = F, warning = F}
dat7 <- subset(dat, R0==4 & phaseI==0.38)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat7) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ dStart) +
  ggtitle("Symptomatic Infections (R0 4)") +
  #coord_cartesian(ylim=c(0, 700000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat7) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 4)") + 
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 17000)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat7) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 4)") +
  facet_wrap(. ~ dStart) +
  #coord_cartesian(ylim=c(0, 4291)) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented at Day Indicated") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### Assuming current interventions are 38% effective and we change this in 10 days to be more or less strict. Each graph is a different R0, indicated at the top.

```{r, echo = F, message = F, warning = F}
dat8 <- subset(dat, phaseI==0.38 & dStart==72)

#pdf('./infections.pdf')
ggplot(data = dat8) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ R0) +
  ggtitle("Symptomatic Infections") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat8) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations") + 
  facet_wrap(. ~ R0) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat8) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care") +
  facet_wrap(. ~ R0) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat8) +
  geom_line(mapping = aes(x = date, y = D, color = as.factor(mag))) +
  facet_wrap(. ~ R0) +
  ggtitle("Deaths") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Deaths") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

### Tables below assume 38% current effectiveness of SD. Mean, min and max are across varying levels of R0.

#### Expected numbers of infected, hospitalized and critical care by June 1, 2020 and January 1, 2021, by social distancing measures beginning **Monday**.

```{r, echo = F, message = F, warning = F}
library(dplyr)

dat$june <- ifelse(dat$date == as.Date('2020-06-01'), 0, NA)
dat$june <- ifelse(dat$date == as.Date('2021-01-01'), 1, dat$june)

tab <- dat %>%
  group_by(mag, dStart, R0, june, phaseI) %>%
  summarise(
    I = sum(I, na.rm = TRUE),
    CC = sum(Ic, na.rm = TRUE),
    H = sum(Ih, na.rm = TRUE), 
    R = sum(R, na.rm = TRUE), 
    Rc = sum(Rc, na.rm = TRUE),
    Rh = sum(Rh, na.rm = TRUE),
    D = sum(D, na.rm = TRUE)
  ) 

tab1 <- subset(tab, dStart==62 & is.na(june)==F & phaseI == .38)
tab1$inf <- tab1$R+tab1$I+tab1$H+tab1$CC
m <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), mean), 0)
min <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), min), 0)
max <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), max), 0)

c1 <- cbind(m[,1], min[,1], max[,1], m[,2], min[,2], max[,2])
colnames(c1) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1, caption="Infections (range of R0: 2.5-4.0)")

tab1$allhosp <- tab1$Rh+tab1$H
m3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), mean), 0)
min3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), min), 0)
max3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), max), 0)

c1.3 <- cbind(m3[,1], min3[,1], max3[,1], m3[,2], min3[,2], max3[,2])
colnames(c1.3) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.3, caption="Hospitalized (range of R0: 2.5-4.0)")

tab1$allcc <- tab1$Rc+tab1$CC
m2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), mean), 0)
min2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), min), 0)
max2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), max), 0)

c1.2 <- cbind(m2[,1], min2[,1], max2[,1], m2[,2], min2[,2], max2[,2])
colnames(c1.2) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.2, caption="Critical care (range of R0: 2.5-4.0)")

tab1$d <- tab1$D
m4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), mean), 0)
min4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), min), 0)
max4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), max), 0)

c1.4 <- cbind(m4[,1], min4[,1], max4[,1], m4[,2], min4[,2], max4[,2])
colnames(c1.4) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.4, caption="Deaths (range of R0: 2.5-4.0)")

```

#### Expected numbers of infected, hospitalized and critical care by June 1, 2020 and January 1, 2021, by social distancing measures beginning **5 days from Monday**.

```{r, echo = F, message = F, warning = F}
tab1 <- subset(tab, dStart==67 & is.na(june)==F & phaseI == .38)
tab1$inf <- tab1$R+tab1$I+tab1$H+tab1$CC
m <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), mean), 0)
min <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), min), 0)
max <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), max), 0)

c1 <- cbind(m[,1], min[,1], max[,1], m[,2], min[,2], max[,2])
colnames(c1) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1, caption="Infections (range of R0: 2.5-4.0)")


tab1$allhosp <- tab1$Rh+tab1$H
m3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), mean), 0)
min3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), min), 0)
max3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), max), 0)

c1.3 <- cbind(m3[,1], min3[,1], max3[,1], m3[,2], min3[,2], max3[,2])
colnames(c1.3) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.3, caption="Hospitalized (range of R0: 2.5-4.0)")

tab1$allcc <- tab1$Rc+tab1$CC
m2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), mean), 0)
min2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), min), 0)
max2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), max), 0)

c1.2 <- cbind(m2[,1], min2[,1], max2[,1], m2[,2], min2[,2], max2[,2])
colnames(c1.2) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.2, caption="Critical care (range of R0: 2.5-4.0)")
```

#### Expected numbers of infected, hospitalized and critical care by June 1, 2020 and January 1, 2021, by social distancing measures beginning **10 days from Monday**.

```{r, echo = F, message = F, warning = F}
tab1 <- subset(tab, dStart==72 & is.na(june)==F & phaseI == .38)
tab1$inf <- tab1$R+tab1$I+tab1$H+tab1$CC
m <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), mean), 0)
min <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), min), 0)
max <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), max), 0)

c1 <- cbind(m[,1], min[,1], max[,1], m[,2], min[,2], max[,2])
colnames(c1) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1, caption="Infections (range of R0: 2.5-4.0)")


tab1$allhosp <- tab1$Rh+tab1$H
m3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), mean), 0)
min3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), min), 0)
max3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), max), 0)

c1.3 <- cbind(m3[,1], min3[,1], max3[,1], m3[,2], min3[,2], max3[,2])
colnames(c1.3) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.3, caption="Hospitalized (range of R0: 2.5-4.0)")

tab1$allcc <- tab1$Rc+tab1$CC
m2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), mean), 0)
min2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), min), 0)
max2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), max), 0)

c1.2 <- cbind(m2[,1], min2[,1], max2[,1], m2[,2], min2[,2], max2[,2])
colnames(c1.2) <- c("June mean", "June min", "June max", "Jan '21 mean", "June min", "Jan max")
kable(c1.2, caption="Critical care (range of R0: 2.5-4.0)")
```