---
title: 'COVID-19 Projections for Colorado'
author: "CONFIDENTIAL - NOT TO BE SHARED WITH THE PRESS"
date: "March 21, 2020"
output:
  html_document: default
  fig_caption: yes
  number_sections: yes
  word_document: default
  pdf_document: default
---

We have developed a susceptible, exposed, infected, recovered model (SEIR) specifically tailored to Colorado's population and current intervention strategies. Many of the parameter values come from published data. We compare different values of R0 and intervention effectiveness (decrease in social distancing) starting March 23, 2020, assuming current interventions cause either 25% reduction in social distance or 38% reduction in social distance (since March 17, 2020). First case was assumed to be 1/21/2020.

```{r, echo = F, message = F, warning = F}
op <- par()
options(width=80)
#emptyenv()
rm(list=ls())

library(knitr)
setwd('/Users/katiecolborn/OneDrive - The University of Colorado Denver/COVID19/Code')

dat <- read.csv('./allscenarios3.csv')

dat$date <- as.Date(dat$time, format="%m/%d/%Y", origin="01/21/2020")

dat <- subset(dat, dStart==62)
```

#### R0 2.5 

```{r, echo = F, message = F, warning = F}
dat2 <- subset(dat, R0==2.5)

library(ggplot2)
require(scales)
#pdf('./infections.pdf')
ggplot(data = dat2) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ phaseI) +
  ggtitle("Symptomatic Infections (R0 2.5)") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat2) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 2.5)") + 
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

For critical care plots, the red horizontal lines indicate 709 ICU beds, 1709 ICU beds and 4291 ICU beds. We assume that 709 beds are not in use currently (out of the ~1400 total across the state). We further assume that 1709 beds will be available (due to expansion) by late April, and 4291 after that. These were estimated by CDPHE. 

```{r, echo = F, message = F, warning = F}

ggplot(data = dat2) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 2.5)") +
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())


```

#### R0 3.0 

```{r, echo = F, message = F, warning = F}
dat4 <- subset(dat, R0==3)

ggplot(data = dat4) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ phaseI) +
  ggtitle("Symptomatic Infections (R0 3)") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat4) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 3)") + 
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat4) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 3)") +
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### R0 4.0 

```{r, echo = F, message = F, warning = F}
dat6 <- subset(dat, R0==4)

ggplot(data = dat6) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ phaseI) +
  ggtitle("Symptomatic Infections (R0 4)") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat6) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations (R0 4)") + 
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat6) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care (R0 4)") +
  facet_wrap(. ~ phaseI) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

#### Assuming current interventions are 38% effective and we change this Monday, March 23, 2020, to be more or less strict. Each graph is a different R0, indicated at the top.

```{r, echo = F, message = F, warning = F}
dat8 <- subset(dat, phaseI==0.38)

#pdf('./infections.pdf')
ggplot(data = dat8) +
  geom_line(mapping = aes(x = date, y = I, color = as.factor(mag))) +
  facet_wrap(. ~ R0) +
  ggtitle("Symptomatic Infections") +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Symptomatic Infections") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
#invisible(dev.off())

ggplot(data = dat8) +
  geom_line(mapping = aes(x = date, y = Ih, color = as.factor(mag))) +
  ggtitle("Hospitalizations") + 
  facet_wrap(. ~ R0) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Hospitalizations") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

ggplot(data = dat8) +
  geom_hline(yintercept=709, linetype="dashed", color = "red") +
  geom_hline(yintercept=1709, linetype="dashed", color = "red") +
  geom_hline(yintercept=4291, linetype="dashed", color = "red") +
  geom_line(mapping = aes(x = date, y = Ic, color = as.factor(mag))) +
  ggtitle("Critical Care") +
  facet_wrap(. ~ R0) +
  scale_y_continuous(labels = comma, breaks = scales::pretty_breaks(n = 10)) +
  ylab("Critical Care") +
  xlab("Date") +
  labs(color="Social Distancing Implemented") +
  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())

#ggplot(data = dat8) +
#  geom_line(mapping = aes(x = date, y = D, color = #as.factor(mag))) +
#  facet_wrap(. ~ R0) +
#  ggtitle("Deaths") +
#  scale_y_continuous(labels = comma, breaks = #scales::pretty_breaks(n = 10)) +
#  ylab("Deaths") +
#  xlab("Date") +
#  labs(color="Social Distancing Implemented") +
#  scale_x_date(date_labels="%b %y",date_breaks  ="2 month") +
#  theme(legend.position="bottom", legend.box = "horizontal", axis.text.x = element_text(angle = 90), panel.background = element_blank(), legend.key=element_blank())
```

### Tables below assume 38% current effectiveness of social distancing (SD). Mean, min and max are across varying levels of R0.

#### Expected cumulative numbers of infected, hospitalized and critical care by June 1, 2020 and January 1, 2021, by social distancing measures beginning Monday, March 23, 2020.

```{r, echo = F, message = F, warning = F}
library(dplyr)

dat$june <- ifelse(dat$date == as.Date('2020-06-01'), 0, NA)
dat$june <- ifelse(dat$date == as.Date('2021-01-01'), 1, dat$june)

tab <- dat %>%
  group_by(mag, R0, june, phaseI) %>%
  summarise(
    I = sum(I, na.rm = TRUE),
    CC = sum(Ic, na.rm = TRUE),
    H = sum(Ih, na.rm = TRUE), 
    R = sum(R, na.rm = TRUE), 
    Rc = sum(Rc, na.rm = TRUE),
    Rh = sum(Rh, na.rm = TRUE),
    D = sum(D, na.rm = TRUE)
  ) 

tab1 <- subset(tab, is.na(june)==F & phaseI == .38)
tab1$inf <- tab1$R+tab1$I+tab1$H+tab1$CC + tab1$Rc + tab1$Rh
m <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), mean), 0)
min <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), min), 0)
max <- round(tapply(tab1$inf, list(tab1$mag, tab1$june), max), 0)

c1 <- cbind(m[,1], min[,1], max[,1], m[,2], min[,2], max[,2])
colnames(c1) <- c("June mean", "June min", "June max", "Jan '21 mean", "Jan min", "Jan max")
kable(c1, caption="Infections (range of R0: 2.5-4.0)")

tab1$allhosp <- tab1$Rh+tab1$H
m3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), mean), 0)
min3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), min), 0)
max3 <- round(tapply(tab1$allhosp, list(tab1$mag, tab1$june), max), 0)

c1.3 <- cbind(m3[,1], min3[,1], max3[,1], m3[,2], min3[,2], max3[,2])
colnames(c1.3) <- c("June mean", "June min", "June max", "Jan '21 mean", "Jan min", "Jan max")
kable(c1.3, caption="Hospitalized (range of R0: 2.5-4.0)")

tab1$allcc <- tab1$Rc+tab1$CC
m2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), mean), 0)
min2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), min), 0)
max2 <- round(tapply(tab1$allcc, list(tab1$mag, tab1$june), max), 0)

c1.2 <- cbind(m2[,1], min2[,1], max2[,1], m2[,2], min2[,2], max2[,2])
colnames(c1.2) <- c("June mean", "June min", "June max", "Jan '21 mean", "Jan min", "Jan max")
kable(c1.2, caption="Critical care (range of R0: 2.5-4.0)")

tab1$d <- tab1$D
m4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), mean), 0)
min4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), min), 0)
max4 <- round(tapply(tab1$d, list(tab1$mag, tab1$june), max), 0)

c1.4 <- cbind(m4[,1], min4[,1], max4[,1], m4[,2], min4[,2], max4[,2])
colnames(c1.4) <- c("June mean", "June min", "June max", "Jan '21 mean", "Jan min", "Jan max")
#kable(c1.4, caption="Deaths (range of R0: 2.5-4.0)")

```

